### 2022-08-10 doc/src/IMSIC.tex
Improve text about the arrangement of IMSIC pages in memory
Especially clarify that these are all recommendations, not
requirements.

If an IMSIC implements guest interrupt files, the memory pages for the
IMSIC's supervisor-level interrupt file and for its guest interrupt
files are contiguous, starting with the supervisor-level interrupt
file at the lowest address and followed by the guest interrupt files,
ordered by guest interrupt number.
Schematically, the memory pages are ordered contiguously as
\begin{displayLinesTable}
S,\, $\mbox{G}_{1}$, $\mbox{G}_{2}$, $\mbox{G}_{3}$, \dots
\end{displayLinesTable}
where S~is the page for the supervisor-level interrupt file and each
$\mbox{G}_{i}$ is the page for the interrupt file of guest interrupt
number~$i$.
Consequently, the smallest that constant $D$ can be is
${\lceil\log_{\rm 2}(\mbox{maximum GEILEN}+\mbox{1})\rceil}+12$,
recalling that GEILEN for each IMSIC is the number of guest interrupt
files the IMSIC implements.

@@

When a system divides harts into groups, each in its own
separate portion of the address space, the memory page
addresses of interrupt files are expected to follow the formulas
${g\times\mbox{2}^{E}}+A+{h\times\mbox{2}^{C}}$ for machine-level
interrupt files, and ${g\times\mbox{2}^{E}}+B+{h\times\mbox{2}^{D}}$
for supervisor-level interrupt files, with $g$ being a
\emph{group number}, $h$ being a hart number relative to the group,
and $E$ being another integer constant $\geq$~${k+\max(C,D)}$ but
usually significantly larger.
If the largest group number is $g_{\rm max}$, let
${j = \lceil\log_{2}(g_{\rm max}+\mbox{1})\rceil}$, the number of bits
needed to represent any group number.
Besides being multiples of $\mbox{2}^{k+C}$ and $\mbox{2}^{k+D}$
respectively, $A$ and $B$ should be chosen so
\begin{displayLinesTable}[lll]
$\left((\mbox{2}^{j}-\mbox{1})\times\mbox{2}^{E}\right)$ \z{\&} $A \,=\, 0$ &
  and &
  $\left((\mbox{2}^{j}-\mbox{1})\times\mbox{2}^{E}\right)$ \z{\&} $B \,=\, 0$
\end{displayLinesTable}
where the ampersands (\z{\&}) represent bitwise logical AND.
This ensures that
\begin{displayLinesTable}[lcll]
$g\times\mbox{2}^{E}+A+h\times\mbox{2}^{C}$ & always equals &
  $(g\times\mbox{2}^{E})$ \z{|} $A$ \z{|} $(h\times\mbox{2}^{C})$, & and\\
$g\times\mbox{2}^{E}+B+h\times\mbox{2}^{D}$ & always equals &
  $(g\times\mbox{2}^{E})$ \z{|} $B$ \z{|} $(h\times\mbox{2}^{D})$.\\
\end{displayLinesTable}

The requirements for read-only-zero pages apply only within each group.
Specifically, if $g$ is any integer between 0 and ${\mbox{2}^{j}-1}$
inclusive, then within the address ranges,
\begin{displayLinesTable}[lcll]
$g\times\mbox{2}^{E}+A$ & through &
  $g\times\mbox{2}^{E}+A+\mbox{2}^{k+C}-\mbox{1}$, &
  and\\
$g\times\mbox{2}^{E}+B$ & through &
  $g\times\mbox{2}^{E}+B+\mbox{2}^{k+D}-\mbox{1}$,\\
\end{displayLinesTable}
pages not occupied by an interrupt file should be read-only zeros.

>>>>

If an IMSIC implements guest interrupt files, the memory pages for the
IMSIC's supervisor-level interrupt file and for its guest interrupt
files should be contiguous, starting with the supervisor-level interrupt
file at the lowest address and followed by the guest interrupt files,
ordered by guest interrupt number.
Schematically, the memory pages should be ordered contiguously as
\begin{displayLinesTable}
S,\, $\mbox{G}_{1}$, $\mbox{G}_{2}$, $\mbox{G}_{3}$, \dots
\end{displayLinesTable}
where S~is the page for the supervisor-level interrupt file and each
$\mbox{G}_{i}$ is the page for the interrupt file of guest interrupt
number~$i$.
Consequently, the smallest that constant $D$ can be is
${\lceil\log_{\rm 2}(\mbox{maximum GEILEN}+\mbox{1})\rceil}+12$,
recalling that GEILEN for each IMSIC is the number of guest interrupt
files the IMSIC implements.

@@

When a system divides harts into groups, each in its own
separate portion of the address space, the memory page
addresses of interrupt files should follow the formulas
${g\times\mbox{2}^{E}}+A+{h\times\mbox{2}^{C}}$ for machine-level
interrupt files, and ${g\times\mbox{2}^{E}}+B+{h\times\mbox{2}^{D}}$
for supervisor-level interrupt files, with $g$ being a
\emph{group number}, $h$ being a hart number relative to the group,
and $E$ being another integer constant $\geq$~${k+\max(C,D)}$ but
usually much larger.
If the largest group number is $g_{\rm max}$, let
${j = \lceil\log_{2}(g_{\rm max}+\mbox{1})\rceil}$, the number of bits
needed to represent any group number.
Besides being multiples of $\mbox{2}^{k+C}$ and $\mbox{2}^{k+D}$
respectively, $A$ and $B$ should be chosen so
\begin{displayLinesTable}[lll]
$\left((\mbox{2}^{j}-\mbox{1})\times\mbox{2}^{E}\right)$ \z{\&} $A \,=\, 0$ &
  and &
  $\left((\mbox{2}^{j}-\mbox{1})\times\mbox{2}^{E}\right)$ \z{\&} $B \,=\, 0$
\end{displayLinesTable}
where an ampersand (\z{\&}) represents bitwise logical AND.
This ensures that
\begin{displayLinesTable}[lcll]
$g\times\mbox{2}^{E}+A+h\times\mbox{2}^{C}$ & always equals &
  $(g\times\mbox{2}^{E})$ \z{|} $A$ \z{|} $(h\times\mbox{2}^{C})$, & and\\
$g\times\mbox{2}^{E}+B+h\times\mbox{2}^{D}$ & always equals &
  $(g\times\mbox{2}^{E})$ \z{|} $B$ \z{|} $(h\times\mbox{2}^{D})$.\\
\end{displayLinesTable}

Infilling with read-only-zero pages is expected
only within each group, not between separate groups.
Specifically, if $g$ is any integer between 0 and ${\mbox{2}^{j}-1}$
inclusive, then within the address ranges,
\begin{displayLinesTable}[lcll]
$g\times\mbox{2}^{E}+A$ & through &
  $g\times\mbox{2}^{E}+A+\mbox{2}^{k+C}-\mbox{1}$, &
  and\\
$g\times\mbox{2}^{E}+B$ & through &
  $g\times\mbox{2}^{E}+B+\mbox{2}^{k+D}-\mbox{1}$,\\
\end{displayLinesTable}
pages not occupied by an interrupt file should be read-only zeros.
